%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Linux kernel Bug Fixing Summer 2022} % Job title
    {The Linux Foundation} % Organization
    {Remote Intership} % Location
    {Jun. 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn the tools usage, programming specifications and patch development process in Linux kernel development}
        \item {Participate in the submission of \textbf{seven} patches, and \href{https://git.kernel.org/pub/scm/linux/kernel/git/torvalds/linux.git/log/?qt=grep&q=hawkins+jiawei}{\textcolor{awesome-skyblue}{five}} of them are merged into the mainline}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Kernel Development} % Job title
    {kernel Development Community} % Organization
    {Kernel Mailing Lists} % Location
    {Sept. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn the knowledge about the network subsystem, and fix \href{https://git.kernel.org/pub/scm/linux/kernel/git/torvalds/linux.git/commit/?id=399ab7fe0fa0d846881685fd4e57e9a8ef7559f7}{\textcolor{awesome-skyblue}{memory leak in tcindex}}}
        \item {Learn the knowledge about the file subsystem, and fix \href{https://git.kernel.org/pub/scm/linux/kernel/git/torvalds/linux.git/commit/?id=d85a1bec8e8d552ab13163ca1874dcd82f3d1550}{\textcolor{awesome-skyblue}{out-of-bounds read in NTFS}}}
        \item {Analyze and debug the \textbf{poc for kernel crashes} and try to fix the problem. Approximately \href{https://git.kernel.org/pub/scm/linux/kernel/git/torvalds/linux.git/log/?qt=author&q=hawkins+jiawei}{\textcolor{awesome-skyblue}{more than ten patches}} are merged into the mainline}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {openEuler Intership} % Job title
    {openEuler Community} % Organization
    {Remote Intership} % Location
    {Jan. 2023 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implement variable\textbf{configurable granularity memory data address alignment} based on classic flang}
        \item {Merged patches into the \href{https://gitee.com/src-openeuler/flang/commits/master?user=yinjiawei2023}{\textcolor{awesome-skyblue}{openEuler community}} and \href{https://github.com/flang-compiler/flang/commit/7f17301a9715e229fc19242802e1bff953967d3e}{\textcolor{awesome-skyblue}{GitHub community}} respectively.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Google Summer of Code} % Job title
    {QEMU Community} % Organization
    {Remote Intership} % Location
    {May. 2023 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn the knowledge about the SVQ, identify and fix multiple issues related to SVQ}
        \item {Implement \href{https://summerofcode.withgoogle.com/archive/2023/projects/zptoHp3v}{\textcolor{awesome-skyblue}{virtio-net CVQ state restore}}}
        \item {Optimize the performance of CVQ state restore for vdpa, enabling parallel restore of CVQ states post live migration, as opposed to sequential restore}
        \item {\href{https://gitlab.com/qemu-project/qemu/-/commits/master?search=Hawkins\%20Jiawei}{\textcolor{awesome-skyblue}{Multiple patches}} are merged into the master branch}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
